\begin{cvcontentsection}{Publications \& Working Papers}

\cvpublication
    {Assessing Risk in Long-term CO\textsubscript{2} Storage Under Uncertainty via Survival Analysis-based Surrogates}
    {\textbf{Gurwicz, A.}, Chen, J., Gutman, D. H., Gildin, E.}
    {\textit{SPE Journal} \textbf{30} (05): 2837--2854. \cvdoilink{10.2118/220737-PA}}
    [2025]

\cvpublication*
    {Solving the Substitution-tolerant Subgraph Isomorphism Problem}
    {Cardoso, I., \textbf{Gurwicz, A.}, Validi, H., Gutman, D. H.}
    {\textit{In preparation for submission to INFORMS Journal on Optimization}.}
    [2025]

\end{cvcontentsection}

\begin{cvcontentsection}{Patents}

\cvpublication
    {Systems and Methods for Identifying and Alerting of Footprint Over-Cycle Risks on Multi-Product General Assembly
    Lines}
    {Carroll, D. J., Wiley, C. A., Danda, S. R. K., Jeet, V., Remutula, P., Clark, K. A., Morrow, M., Gutman, D. H.,
    \textbf{Gurwicz, A.}, Fernandes, G. L. N.}
    {\textit{Patent filed with the USPTO on 03/13/2023 and published on 09/19/2024 under no.\ US 2024/0308781 A1. Pending.}}

\cvpublication*
    {Methods for Simulating Conveyor Cycles on Multi-Product General Assembly Lines}
    {Carroll, D. J., Wiley, C. A., Jeet, V., Finnin, A., Clark, K. A., Morrow, M., Gutman, D. H., Chen, L.,
    \textbf{Gurwicz, A.}, Fernandes, G. L. N., Zaman, M., Nguyen, N.}
    {\textit{Patent filed with the USPTO on 03/13/2023 and published on 09/19/2024 under no.\ US 2024/0311730 A1. Pending.}}

\end{cvcontentsection}

\begin{cvcontentsection}[%
    \begin{cvswitchfont}{\publicationauthorsize}(\( \ast \) denotes presenting author)\end{cvswitchfont}%
]{Proceedings}

\cvpublication
    {Advancing Surrogate Modeling For CO\textsubscript{2} Storage Risk Through Cutting-edge Survival Analysis-driven AI}
    {\textbf{Gurwicz, A.}, Gutman, D. H., Gildin, E.}
    {\textit{Accepted to IPTC Summit on AI for the Energy Industry}, Dubai, UAE.}
    [2026]

\cvpublication
    {Transient Dynamics Simulation Platform For PDC, Roller Cone, And Hybrid Bits Utilizing Discrete Geometry}
    {Endres, L., \textbf{Gurwicz, A.}, Pansare, O., Akindele, O., Mada, H., Jones, J., Cheng, C., Mukkirwar, R.}
    {\textit{Accepted to Abu Dhabi International Petroleum Exhibition and Conference (ADIPEC)}, Abu Dhabi, UAE.}
    [2025]

\cvpublication
    {Assessing Risk in Long-term CO\textsubscript{2} Storage Under Uncertainty via Survival Analysis-based Surrogates}
    {\textbf{Gurwicz, A.}*, Chen, J., Gutman, D. H., Gildin, E.}
    {\textit{SPE Annual Technical Conference and Exhibition (ATCE)}, New Orleans, Louisiana, USA. \cvdoilink{10.2118/220737-MS}}
    [2024]

\cvpublication
    {Smart Well Data Generation via Boundary-Seeking Deep Convolutional Generative Adversarial Networks}
    {\textbf{Gurwicz, A.}*, Canchumuni, S. A., Pacheco, M. A. C.}
    {\textit{International Conference on Artificial Intelligence and Soft Computing (ICAISC)}, Zakopane, Poland. \cvdoilink{10.1007/978-3-030-20912-4\_7}}
    [2019]

\cvpublication
    {Forecasting Smart Well Production via Deep Learning and Data Driven Optimization}
    {Calvette, T., \textbf{Gurwicz, A.}*, Abreu, A. C. A., Pacheco, M. A. C.}
    {\textit{Offshore Technology Conference (OTC) Brasil}, Rio de Janeiro, Brazil. \cvdoilink{10.4043/29861-MS}}
    [2019]

\cvpublication
    {LSTM Networks and Box-Jenkins Models Applied to Load Forecasting for a Southeastern Brazil Giant Energy Consumer (in Portuguese)}
    {Nunes, A., da Conceição, L., Mendoza, L. F., de Mello Jr., H. D.*, \textbf{Gurwicz, A.}, Figueiredo, K.}
    {\textit{14th Brazilian Congress on Computational Intelligence (CBIC)}, Belém, Brazil. \cvdoilink{10.21528/CBIC2019-100}}
    [2019]

\cvpublication*
    {Hourly Load Forecasting as a Parameter for a Short-Term Pricing and Hydrothermal Dispatch Model (in Portuguese)}
    {da Silva, M., dos Santos, P., Mendoza, L. F., de Mello Jr., H. D.*, \textbf{Gurwicz, A.}}
    {\textit{14th Brazilian Congress on Computational Intelligence (CBIC)}, Belém, Brazil. \cvdoilink{10.21528/CBIC2019-96}}
    [2019]

\end{cvcontentsection}

\begin{cvcontentsection}{Invited Talks}

\cvtalk
    {Survival Analysis Framework for CO\textsubscript{2} Risk Assessment}
    {\textit{Computational Reservoir Engineering (CoRE) Consortium meeting} at Texas A\&M University.}
    {March 2025}

\cvtalk
    {Assessing Risk in Long-term CO\textsubscript{2} Storage Under Uncertainty via Survival Analysis-based Surrogates}
    {\textit{INFORMS student chapter seminar} at Texas Tech University.}
    {February 2025}

\cvtalk
    {A Smart-Well-Centered Investigation into Deep Generative Models for Reservoir Data}
    {\textit{II Seminar of Artificial Intelligence Applied to the Oil \& Gas Industry} at the Brazilian Association of Petroleum Geologists.}
    {November 2020}

\cvtalk*
    {Optimization of Offshore Oil and Gas Production Systems During Design Phase}
    {\textit{I Seminar of Artificial Intelligence Applied to the Oil \& Gas Industry} at the Brazilian Association of Petroleum Geologists.}
    {November 2019}

\end{cvcontentsection}
